Synthesis of production rules for glycans

### 2020-10-16 papers/sugar-synth/experiments.tex
some space saving

In this section, we  present our implementation of the proposed method for the synthesis
and discuss the interesting optimizations in the implementation.
%
We also apply our tool on several data sets and illustrate the usability of our method.

{\em Implementation:} 
We have implemented method \textsc{SugarSynth} in a prototype tool {\ourtool} for
analyzing the performance of the technique in practice.
%
The tool, written in {\tt C++}, uses {\zthree}\cite{z3} as the SMT solver
to discharge the generated satisfiability queries.
%
% We have developed a specialized file format for giving input to~\ourtool.
% %
% The format allows one to declare monomers, list molecules over the monomers
% in the SMTLIB like format,
% and pass the input parameters of the method.

>>>>

In this section, we  present our implementation of the proposed method.
We also apply our tool on several data sets and illustrate the usability of our method.

{\em Implementation:} 
We have implemented method \textsc{SugarSynth} in a prototype tool {\ourtool}.
%
The tool, written in {\tt C++}, uses {\zthree}\cite{z3} as the SMT solver
to discharge the generated satisfiability queries.
%
% We have developed a specialized file format for giving input to~\ourtool.
% %
% The format allows one to declare monomers, list molecules over the monomers
% in the SMTLIB like format,
% and pass the input parameters of the method.
